FoRTE baseline

### 2019-01-30 analysis/paper/paper.Rmd
PAPER: Finish the list of ED2 schemes

- Soil decomposition (`DECOMP_SCHEME`)

@@

@@

>>>>

- Soil decomposition temperature sensitivity (`DECOMP_SCHEME`)

@@

- Carbon balance contribution to mortality (`IDDMORT_SCHEME`)
        - (0, default): Carbon balance in terms of fluxes only
        - (1) Carbon balance is offset by storage pool (i.e. carbon storage is an additional buffer against mortality)
    - Additional protection from (1) should reduce mortality for all trees, so will probably reinforce dominance of early successional trees?
    - But likely to interact with other schemes, especially structural growth, which determines size of NSC reserves
- Carbon stress scheme (`CBR_SCHEME`)
        - (0, default): Single stress, with maximum carbon balance determined at full sun and no moisture
        - (1) Co-limitation of light and moisture; calculate `cb/cb_lightmax` and `cb/cb_moistmax`, and weight based on `DDMORT_CONST` (tunable global[?] parameter)
        - (2) "Leibig style"; limitation based on whether soil or light are more important (`cb/max(cb_lightmax, cb_moistmax)`)
    - No idea about this one. Need to do more reading.
- Quantum yield model (`QUANTUM_EFFICIENCY_T`)
        - (0, default): Constant quantum efficiency
        - (1): Quantum efficiency varies with temperature, based on Ehleringer (1978) (TODO: Get ref)
    - Uncertainty should increase with (1) assuming parameters are tunable. 
    - Depends on where UMBS conditions fall within the range of temperatures. Good candidate for exploratory analysis outside of ED.
- Nitrogen limitation of photosynthesis (`N_PLANT_LIM`)
        - (0, default): No limitation
        - (1) Limitation based on internal model (TODO: what is it?)
    - Turning this on _should_ favor mid-successional species, and substantially increase uncertainty.
- Nitrogen limitation of decomposition (`N_PLANT_LIM`)
        - (0, default): No limitation
        - (1) Limitation based on internal model (TODO: what is it?)
    - Same as above
- Canopy roughness model (`ICANTURB`)
        - (0): Based on Leuning et al. (1995; TODO REF). Wind computed using "similarity theory" for top cohort, then extinguished with cumulative LAI.
        - (1, default) "Default ED2.1 scheme" (TODO: 0? Figure it out!), but using "zero-plane" displacement height.
        - (2) Massman (1997; TODO) using constant drag and no sheltering factor
        - (3) Also Massman, but with varying drag and sheltering within canopy
        - (4) Like 0, but calculate ground conductance following CLM (eq. 5.98-5.100)
    - No idea, except that (3) will have higher uncertainty than (2). Need to read more about this.
- Similarity theory model (for canopy roughness) (`ISFCLYRM`)
    - Computes `u*`, `T*`, etc.
        - (1) BRAMS default, based on Louis (1979 TODO). 
        - (2) Oncley and Dudhia (1995 TODO), based on MM5
        - (3) Beljaars and Holtslag (1991 TODO); Like (2), but alternative method for stable case that has more mixing
        - (4, default) CLM (2004; TODO: Check that this is same as 2013?). Like (2) and (3), but with special functions to deal with very stable cases.
    - Again, no idea. Need to read more about micro-meteorology and how it affects vegetation processes.
- Ground to canopy conductance (`IED_GRNDVAP`)
        - (0, default): Modified Lee Pielke (1992 TODO), with field capacity, but with beta factor without square (as in Noilhan and Planton 1989 TODO). Like original ED2 and LEAF-3.
        - (1-4) Mahfouf and Noilhan (1991 TODO), #1-4
        - (5) Combination of (1) (alpha) and (2) (soil resistance)
    - No idea. Again, need to do some micro-met reading.
- Percolation and infiltration (`IPERCOL`)
        - (0) Constant soil conductivity. Temporary surface water (only exists if top soil layer is saturated) exceeding 1:9 liquid:ice ratio shed via percolation.
        - (1, default) Constant soil conductivity, with percolation model from Anderson (1976 NOAA technical report NWS 19 TODO). Temporary surface water can exist after heavy rain event even if soil doesn't saturate.
        - (2) Like (1), but soil conductivity decreases with depth even under constant soil moisture
    - Presumably, not a huge impact at UMBS because water shouldn't be an issue.
    - See also `RUNOFF_TIME` (e-folding lifetime of temporary surface water)
- Tree-fall disturbance rate (`TREEFALL_DISTURBANCE_RATE`)
        - (0, default) No treefall disturbance
        - (> 0) Disturbance rate, in 1/years. Will create new patches.
        - (< 0) Also rate, but will be added to mortality (kill plants, but no new patches)
    - Reference value for this is 0.014 trees year^-1^ (note that because of ED's cohort approximation, number of individuals is continuous, not discrete)
    - See also `TIME2CANOPY`, minimum age for tree-fall disturbance.
- Growth respiration (`GROWTH_RESP_SCHEME`)
        - (0, default) Growth respiration is a tax on GPP, at PFT-specific rate. Treated as aboveground wood to canopy-airspace flux.
        - (1) Growth respiration calculated as in (0), but split into leaf, sapwood-a, sapwood-b, and root sources proportionally to biomass. No effect on overall C budget, but greater within-ecosystem flux resolution.
    - These should produce identical results, and if they don't, that means there is a bug!
    - If output is identical, we should set to (1), since we can always calculate total respiration otherwise.
- Storage respiration (`STORAGE_RESP_SCHEME`) -- same as growth
    - Note that this whole system is a _hack_, because there is no real "storage respiration" process. In PEcAn, we hard-code the relevant parameters to zero. An interesting question is whether we may be able to get better results with this hack enabled -- i.e. if it compensates a problem in some other process.

@@

    - Fire disturbance (`INCLUDE_FIRE`) -- We know there weren't any fires at UMBS during this time, and more generally are interested in stability.
        - This could potentially be fun to play with in a later paper about disturbance regimes. Potentially, with Jackie Matthes?
    - Anthropogenic disturbances (`IANTH_DISTURB`) -- We are currently looking at stable state, without disturbances. But, since this pulls values from a dataset, this could be one way to apply the FoRTE treatments.
